---
title: "Untitled"
output: html_document
---
Firstly we should load dplyr package, it'll help us to manage datasets in more
convenient way.
```{r}
library(dplyr)
```

Let's read our table.
```{r}
info <- tbl_df(read.csv("activity.csv"))
```

Ok. To retrieve useful information, we should group our dataframe
by date and create new dataset with total amount of steps each day, average
amount of steps and median.
```{r}
info_grouped_by_day <- group_by(info, date)
info_by_day <- summarise(info_grouped_by_day, total_steps = sum(steps),
      average_steps = mean(steps, na.rm = TRUE, median_steps = median(steps)))

hist(info_by_day$total_steps)
```
We've done great work! Let's continue!

So now it'll be good to group main dataframe by time, and create new dataframe
with useful information.
```{r}
info_grouped_by_time <- group_by(info, interval)
info_by_time <- summarise(info_grouped_by_time, 
      average_steps = mean(steps, na.rm = TRUE))

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
